Target Markdown

### 2024-01-07 _targets.Rmd
final edits

```{r, engine="targets", data_import}
list(

  tarchetypes::tar_download(ids_path,
      urls = Sys.getenv("link_to_supervisors"),
      paths = here::here("data", "raw", "supervisors.csv")),
  tarchetypes::tar_download(gender_path,
      urls = Sys.getenv("link_to_gender"),
      paths = here::here("data", "raw", "names4api_tagged.tsv")),
  tarchetypes::tar_download(authors_arrow_path,
      urls = Sys.getenv("link_to_updated_authors"),
      paths = here::here("data", "raw", "authors_by_pubs.arrow"),
       mode = "wb"),
  tarchetypes::tar_download(text_arrow_path,
      urls = Sys.getenv("link_to_updated_texts"),
      paths = here::here("data", "raw", "riv_text.arrow"),
      mode = "wb"),
  tarchetypes::tar_download(cep_investigators_path,
      urls = Sys.getenv("link_to_cep_investigators"),
      paths = here::here("data", "raw", "cep_investigators.arrow"),
       mode = "wb"),
  tarchetypes::tar_download(cep_details_path,
      urls = Sys.getenv("link_to_cep_details"),
      paths = here::here("data", "raw", "cep_details.arrow"),
       mode = "wb"),
  tarchetypes::tar_download(riv_details_path,
      urls = Sys.getenv("link_to_riv_details"),
      paths = here::here("data", "raw", "riv_details.arrow"),
       mode = "wb"),
  tarchetypes::tar_download(riv_authors_path,
      urls = Sys.getenv("link_to_riv_authors"),
      paths = here::here("data", "raw", "riv_authors.arrow"),
       mode = "wb"),
   tarchetypes::tar_download(sup_path,
      urls = Sys.getenv("link_to_manual_sup_search"),
      paths = here::here("data", "raw", "manual_sup_search_4.csv")),
  tarchetypes::tar_download(sup_path_second,
      urls = Sys.getenv("link_to_manual_sup_search_second"),
      paths = here::here("data", "raw", "manual_sup_search_second.csv")),
  tarchetypes::tar_download(blacklist_path,
      urls = Sys.getenv("link_to_blacklist_control"),
      paths = here::here("data", "raw", "blacklist_control_after_disamb.csv")),
  tarchetypes::tar_download(all_sup_path,
      urls = Sys.getenv("link_to_all_sup"),
      paths = here::here("data", "raw", "all_sup.csv")),

>>>>

```{r, engine="targets", data_import}
# Set global timeout for download operations
options(timeout = 3000) # 50 minutes

  tarchetypes::tar_download(ids_path,
      urls = Sys.getenv("link_to_supervisors"),
      paths = here::here("data", "raw", "supervisors.csv")),
  tarchetypes::tar_download(gender_path,
      urls = Sys.getenv("link_to_gender"),
      paths = here::here("data", "raw", "names4api_tagged.tsv")),
  tarchetypes::tar_download(authors_arrow_path,
      urls = Sys.getenv("link_to_updated_authors"),
      paths = here::here("data", "raw", "authors_by_pubs.arrow"),
       mode = "wb"),
  tarchetypes::tar_download(text_arrow_path,
      urls = Sys.getenv("link_to_updated_texts"),
      paths = here::here("data", "raw", "riv_text.arrow"),
      mode = "wb"),
  tarchetypes::tar_download(cep_investigators_path,
      urls = Sys.getenv("link_to_cep_investigators"),
      paths = here::here("data", "raw", "cep_investigators.arrow"),
       mode = "wb"),
  tarchetypes::tar_download(cep_details_path,
      urls = Sys.getenv("link_to_cep_details"),
      paths = here::here("data", "raw", "cep_details.arrow"),
       mode = "wb"),
  tarchetypes::tar_download(riv_details_path,
      urls = Sys.getenv("link_to_riv_details"),
      paths = here::here("data", "raw", "riv_details.arrow"),
       mode = "wb"),
  tarchetypes::tar_download(riv_authors_path,
      urls = Sys.getenv("link_to_riv_authors"),
      paths = here::here("data", "raw", "riv_authors.arrow"),
       mode = "wb"),
   tarchetypes::tar_download(sup_path,
      urls = Sys.getenv("link_to_manual_sup_search"),
      paths = here::here("data", "raw", "manual_sup_search_6.csv")),
  tarchetypes::tar_download(sup_path_second,
      urls = Sys.getenv("link_to_manual_sup_search_second"),
      paths = here::here("data", "raw", "manual_sup_search_second.csv")),
  tarchetypes::tar_download(blacklist_path,
      urls = Sys.getenv("link_to_blacklist_control"),
      paths = here::here("data", "raw", "blacklist_control_final_before_disamb.csv")),
  tarchetypes::tar_download(all_sup_path,
      urls = Sys.getenv("link_to_all_sup"),
      paths = here::here("data", "raw", "all_sup.csv")),
